A fast GPU solver for near-Toeplitz tridiagonal systems

### 2015-11-02 paper-draft/paper.tex
add benchmark script
add new results
add more results and update paper draft

\usepackage{amsmath,bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{minted}
\usepackage{xcolor}

@@

\section{3-D compact finite difference on multi-GPU}

%----------------------------------------------------------------------%
\section{Results: single GPU} \label{sec:results-single-gpu}
%----------------------------------------------------------------------%

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/compare-solvers-K20.eps}
\end{center}
\label{fig:compare-solvers-K20}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/compare-solvers-K40.eps}
\end{center}
\label{fig:compare-solvers-K40}
\end{figure}

>>>>

\usepackage{amsmath,bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{multirow}

@@

\pagebreak
%----------------------------------------------------------------------%
\section{Results: single GPU} \label{sec:results-single-gpu}
%----------------------------------------------------------------------%

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-bench-2d.eps}
\end{center}
\label{fig:k20-bench-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-bench-3d.eps}
\end{center}
\label{fig:k20-bench-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-global-vs-shared-2d.eps}
\end{center}
\label{fig:k20-global-vs-shared-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-global-vs-shared-3d.eps}
\end{center}
\label{fig:k20-global-vs-shared-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=250pt]{fig/k20-forward-vs-backward.eps}
\end{center}
\label{fig:k20-forward-vs-backward}
\end{figure}

\input{table/global-vs-shared.tex}
